---
title: "Online_Retail_Yash"
author: "Yash_Patel"
date: "2022-10-31"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# loading the package
library(tidyverse)
# adding dataset
or <-  read.csv("C:/Users/YASH/Downloads/Online_Retail.csv") 

```
# Q1. 
Show the breakdown of the number of transactions by countries i.e., how many transactions are 
in the dataset for each country (consider all records including cancelled transactions). Show this 
in total number and also in percentage. Show only countries accounting for more than 1% of the 
total transactions. 
```{r}
#grouped by the countries and showing the countries with more than 1% of total transaction
or_1 <- group_by(or,Country) %>% summarise( Total_Transactions=length(InvoiceNo)) %>% filter(Total_Transactions > ((nrow(or)) * 1/100))
or_1  

```
# Q2.
Create  a  new  variable  ‘TransactionValue’  that  is  the  product  of  the  exising  ‘Quantity’  and  
‘UnitPrice’ variables. Add this variable to the dataframe. 
```{r}
#adding transaction value column
or_2 <- mutate(or,TransactionValue= Quantity * UnitPrice) #%>% select(Quantity,UnitPrice,Description) %>% filter( UnitPrice < 0)
head(select(or_2, TransactionValue))
```
# Q3.
Using the newly created variable, TransactionValue, show the breakdown of transaction values 
by countries i.e. how much money in total has been spent each country. Show this in total sum of 
transaction values. Show only countries with total transaction exceeding 130,000 British Pound. 
```{r}
#adding TotalTransactionValue column and filtering it for the transaction greater than 130000
or_3 <- group_by(or_2,Country)  %>% summarise(TotalTransactionValue=sum(TransactionValue)) %>% filter(TotalTransactionValue>130000)
or_3
```

# Q4.
```{r}
Temp=strptime(or$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT') 
#head(Temp)

or$New_Invoice_Date <- as.Date(Temp)
#or$New_Invoice_Date[20000]- or$New_Invoice_Date[10] 
or$Invoice_Day_Week= weekdays(or$New_Invoice_Date) 
or$New_Invoice_Hour = as.numeric(format(Temp, "%H")) 
or$New_Invoice_Month = as.numeric(format(Temp, "%m")) 

# a) Show  the  percentage  of  transactions  (by  numbers)  by  days  of  the  week    

or_4.1 <- group_by(or,Invoice_Day_Week) %>% drop_na() %>%  count()
or_4.1$perc <- (or_4.1$n/sum(or_4.1$n)) * 100 
or_4.1

# b) Show the percentage of transactions (by transaction volume) by days of the week 

or_4.2 <- group_by(or,Invoice_Day_Week) %>% select(Invoice_Day_Week,Quantity) %>%  drop_na() %>%  count()
or_4.2$perc <- (or_4.2$n/sum(or_4.2$n)) * 100 
or_4.2

# c) Show the percentage of transactions (by transaction volume) by month of the year 

or_4.3 <- group_by(or,New_Invoice_Month) %>% select(New_Invoice_Month, Quantity) %>% drop_na() %>%  count()
or_4.3$perc <- (or_4.3$n/sum(or_4.3$n)) * 100 
or_4.3

# d) What was the date with the highest number of transactions from Australia? 
or_4.4 <- group_by(or, New_Invoice_Date) %>% drop_na()%>% select(New_Invoice_Date, Country) %>% filter( Country == "Australia" ) %>% count()
max3 <- max(or_4.4$n)
or_4.4.1 <- or_4.4 %>% filter(n == max3)
or_4.4.1

```


# Q5.
Plot  the  histogram  of  transaction  values  from  Germany.  Use  the  hist()  function  to  plot.  
```{r}
#filtering or_2 dataset to select Germany as Country and then selecting Country TransactionValue column 
or_5 <- filter(or_2, Country == "Germany" ) %>% select(Country, TransactionValue)

#assigning variable for histogram 
"Transaction value from Germany" <-  or_5$TransactionValue

#creating histogram using hist function
hist(`Transaction value from Germany`)

```

# Q6.
1.Which customer had the highest number of transactions? 
2.Which customer is most valuable (i.e. highest total sum of transactions)?
```{r}
#1
#counting the total transaction by CustomerID and droping the observation without ColumnID
or_6.0 <- group_by(or_2,CustomerID) %>% summarise( Total_Transactions=length(TransactionValue)) %>% drop_na()

#finding the largest number
max0<- max(or_6.0$Total_Transactions)

#filtering the data to get the CustomerID with Maximum transaction
or_6.0_max <- filter(or_6.0,Total_Transactions== max0)

or_6.0_max

#2
#totaling the TotalTransactionValue by CustomerID and droping the observation without ColumnID
or_6.1 <- group_by(or_2,CustomerID) %>%  summarise(TotalTransactionValue=sum(TransactionValue)) %>% drop_na()

#finding the largest number
max1 <- max(or_6.1$TotalTransactionValue)

#filtering the data to get the CustomerID with Maximum TotalTransactionValue 
or_6.1_max <- filter(or_6.1,TotalTransactionValue== max1)

or_6.1_max  

```
# Q7.
Calculate the percentage of missing values for each variable in the dataset
```{r}
colMeans(is.na(or_2)) #25%(24.92669)


#or

summary(or)
#only ColumnID variable has missing value

or_7 <- (135080*100)/541909

or_7 # ~25%(24.92669)

```

# Q8.
What  are  the  number  of  transactions  with  missing  CustomerID  records  by  countries?
```{r}
#Filtering the Missing CustomeID records and Counting it by Countries under new Column "Total_Transaction"
or_8 <- group_by(or_2,Country ) %>% filter(is.na(CustomerID),Country !="Unspecified") %>% summarise( Total_Transactions=length(CustomerID))

#First Arranging the Total_Transaction in descending order and adding Percentage column showing Total_Transaction in Percentage.
or_8.1 <- or_8 %>% arrange(desc(Total_Transactions)) %>% mutate(percentage = Total_Transactions / sum(Total_Transactions) * 100)
or_8.1
```

# Q9.
On average, how often the costumers comeback to the website for their next shopping? (i.e. what 
is the average number of days between consecutive shopping) 
```{r}
or_9<- or %>% select(CustomerID,New_Invoice_Date) %>% group_by(CustomerID) %>% distinct(New_Invoice_Date) %>% arrange(desc(CustomerID)) %>%  mutate(Days_Between = New_Invoice_Date-lag(New_Invoice_Date)) %>% filter(!is.na(Days_Between)) 
mean(or_9$Days_Between)

```

# Q10.
In the retail sector, it is very important to understand the return rate of the goods purchased by 
customers.  In  this  example,  we  can  define  this  quantity,  simply,  as  the  ratio  of  the  number  of 
transactions cancelled (regardless of the transaction value) over the total number of transactions. 
With  this  definition,  what  is  the  return  rate  for  the  French  customers? 
Consider the cancelled transactions as those where the ‘Quantity’ variable has a negative value
```{r}
#Return  rate  for  the  French  customers

#counting the total number of transaction 
x.0 <-filter(or_2,Country == "France") %>% count()
#counting the transaction with negative quantity
y.0 <-filter(or_2,Country == "France",Quantity < 0) %>% count()
#finally finding the return rate for the french customers dividing the  number  of transactions cancelled over the total number of transactions. 
or_10 <-summarise(or_2, Return_rate_for_the_French_customers= y.0/ x.0 * 100)
or_10 #(1.741264)
```

# Q11.
What is the product that has generated the highest revenue for the retailer? (i.e. item with the 
highest total sum of ‘TransactionValue’).
```{r}
#grouping the dataset by StockCode and using summarise function to find the Total Transaction Value

or_11 <- group_by(or_2, StockCode) %>%  summarise( Total_Transac_val = sum(TransactionValue))
#finding the largest Value
max2 <- max(or_11$Total_Transac_val)
#filtering the dataset to get the Stockcode which has the largest Value
or_11.1 <- filter(or_11,Total_Transac_val==max2)
or_11.1
```


# Q12.
How many unique customers are represented in the dataset?
```{r}
#finding the unique customer using the unique() function and droping the empty observations and then counting the actual unique customers using the count function.
or_12 <- data.frame(unique(or_2$CustomerID)) %>% drop_na() %>% count("Total_Unique_customers")
or_12 

```

